---
output:
  github_document:
    pandoc_args: --webtex=http://chart.apis.google.com/chart?cht=tx&chl=
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Minimal reprexes for `pkgdown` issues

## issue 1397

See `test` vignette: https://indrajeetpatil.github.io/minimalReprex/articles/test.html#issue-1397-1

## issue 1282 (resolved)

Link: https://github.com/r-lib/pkgdown/issues/1282

(Observed at least in `Chrome`. **N.B. Not using netlifly, but rather github pages**)

```{r}
x <- 1 + 2

x
```

## issue 1150 (resolved)

Link: https://github.com/r-lib/pkgdown/issues/1150

Problems with rendering `LaTeX` equations in `README` of `pkgdown` websites.

**This is observed only in Chrome, Internet Explorer, and Edge browsers**. 
No issue with Firefox browser.

This is $\eta_p^2$ (partial eta-squared), but is not rendered properly. 

Exactly how it is rendered depends on which browser you use, but it is rendered
properly only in Firefox.

Somehow this is not an issue when the equations are inside a table:

option-1 | option-2
-------|-------
$\eta_p^2$ | $\omega_p^2$
x | y
1 | 2
